Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-09-21 manuscript/manuscript.tex
Changed arbitrary g function to f function in GLQ description
More fixes to grids issue

\iftwocol{
\begin{equation}
    \begin{split}
        \iiint\limits_\Omega \rho(r') g(r', \phi', \lambda')
        d\Omega \approx& \\
        A
        \sum\limits_{i=1}^{N^r}
        \sum\limits_{j=1}^{N^\phi}
        \sum\limits_{k=1}^{N^\lambda}
        & W_i^r W_j^\phi W_k^\lambda \rho(r_i) g(r_i, \phi_j, \lambda_k),
    \end{split}
\label{eq:glq-var-dens}
\end{equation}
}{
\begin{equation}
    \iiint\limits_\Omega \rho(r') g(r', \phi', \lambda') d\Omega \approx
    A
    \sum\limits_{i=1}^{N^r}
    \sum\limits_{j=1}^{N^\phi}
    \sum\limits_{k=1}^{N^\lambda}
    W_i^r W_j^\phi W_k^\lambda \rho(r_i) g(r_i, \phi_j, \lambda_k),
\label{eq:glq-var-dens}
\end{equation}
}

@@

We compute the gravitational potential ($V$), the vertical component of the gradient
($g_z$), and the diagonal components of the Marussi tensor ($g_{xx}$, $g_{yy}$,
$g_{zz}$) for each of the four tesseroid models and grids in Table
\ref{tab:grids}.
Other components are equal to zero outside of the shell and are thus omitted from the
analysis.
The computations are repeated for values of $D$ ranging from 0.5 to 10 with a step of
0.5.
We then will calculate the maximum absolute difference between these results and the
analytical solutions derived in Appendix \ref{sec:shell}.
The differences are shown in Fig. \ref{fig:D-linear} as relative to the spherical shell
values.
We omit the differences for $g_{xx}$ and $g_{yy}$ because they are equivalent to the
ones obtained for $g_{zz}$.
Finally, we set the optimal value of $D$ as the minimum value at which the corresponding
error of the numerical approximation is lower than 0.1\%.

@@

For an exponential density function, the density-based discretization will be applied
before the adaptive discretization algorithm.
This means that optimal values for both the distance-size ratio $D$ and the delta ratio
$\delta$ must be determined.
We perform an error analysis similar to what was done for the linear density case.
However, we only consider the ``Big Grid'' scenario from Table \ref{tab:grids} for the
sake of brevity.

>>>>

\iftwocol{
\begin{equation}
    \begin{split}
        \iiint\limits_\Omega \rho(r') f(r', \phi', \lambda')
        d\Omega \approx& \\
        A
        \sum\limits_{i=1}^{N^r}
        \sum\limits_{j=1}^{N^\phi}
        \sum\limits_{k=1}^{N^\lambda}
        & W_i^r W_j^\phi W_k^\lambda \rho(r_i) f(r_i, \phi_j, \lambda_k),
    \end{split}
\label{eq:glq-var-dens}
\end{equation}
}{
\begin{equation}
    \iiint\limits_\Omega \rho(r') f(r', \phi', \lambda') d\Omega \approx
    A
    \sum\limits_{i=1}^{N^r}
    \sum\limits_{j=1}^{N^\phi}
    \sum\limits_{k=1}^{N^\lambda}
    W_i^r W_j^\phi W_k^\lambda \rho(r_i) f(r_i, \phi_j, \lambda_k),
\label{eq:glq-var-dens}
\end{equation}
}

@@

We compute the gravitational potential ($V$), the vertical component of the gradient
($g_z$), and the diagonal components of the Marussi tensor ($g_{xx}$, $g_{yy}$,
$g_{zz}$) for each grid in Table \ref{tab:grids}.
Other components are equal to zero outside of the shell and are thus omitted from the
analysis.
The computations are repeated for values of $D$ ranging from 0.5 to 10 with a step of
0.5.
We then will calculate the maximum absolute difference between these results and the
analytical solutions derived in Appendix \ref{sec:shell}.
The differences are shown in Fig. \ref{fig:D-linear} as relative to the spherical shell
values.
We omit the differences for $g_{xx}$ and $g_{yy}$ because they are equivalent to the
ones obtained for $g_{zz}$.
Finally, we set the optimal value of $D$ as the minimum value at which the corresponding
error of the numerical approximation is lower than 0.1\%.

@@

For an exponential density function, the density-based discretization will be applied
before the adaptive discretization algorithm.
This means that optimal values for both the distance-size ratio $D$ and the delta ratio
$\delta$ must be determined.
We perform an error analysis similar to what was done for the linear density case.
However, we only consider the ``Big Grid'' from Table \ref{tab:grids} for the
sake of brevity.
